Modular Inverse Reinforcement Learning on Human Motion

### 2015-02-12 paper.tex
subfigures

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{rldmsubmit,palatino}
\usepackage{graphicx}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5cm]{human.jpg}
\includegraphics[height=5cm]{env.png}
\caption{(Left) A human subject with head tracker, virtual reality displayer, and
body tracker.  (Right) The environment the human can see through the displayer.}
\label{fig:avatar}
\end{figure}

%FIXME
In Figure~\ref{fig:avatar} shows the domain that we use in this paper. The red
cubes represent obstacles, that the agent would be punished if running
into. The blue balls represent targets, that the agent would be rewarded if
collected. There is also a gray path on the ground that the agent can follow.
Naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles.
This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.
We ask human subjects to have trackers and virtual reality displayers equipped. He
can see the envrionment through the displayer in front of his eyes. So he can
walk as if he is walking in the virtual domain.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.24\textwidth]{task_1.png}
\includegraphics[width=0.24\textwidth]{task_2.png}
\includegraphics[width=0.24\textwidth]{task_3.png}
\includegraphics[width=0.24\textwidth]{task_4.png}
\caption{The trajectories of humans and the agent in four different tasks. (Path),
(Obstacle + Path), (Target + Path), (Target + Obstacle + Path), respectively.}
\label{fig:exp}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{contactStats.png}
\caption{Number of targets hit and number of obstacles hit of the human subjects
and the agent.}
\label{fig:heatmap}
\end{figure}

Although humans don't agree each other on how to avoid obstacles or collecting
targets, the agent can figure out what the humans are doing, and perform a
similar trajectory. Table~\ref{tb:human} and Table~\ref{tb:agent} evaluate the
performance by showing the number of targets hit and number of obstacles hit.
Note that the numbers bold-ed are active modules in the corresponding task. We
can observe that humans still do better than the agent in these tasks.

\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth]{objValuesTask1.png}
\includegraphics[width=0.4\textwidth]{objValuesTask2.png}
\includegraphics[width=0.4\textwidth]{objValuesTask3.png}
\includegraphics[width=0.4\textwidth]{objValuesTask4.png}
\caption{Heatmaps of the $\log$ of values of Equation~\ref{eq:irl} for different
weights for the four tasks, respectively. The red zones indicate higher values.
The upper two are Task 1 and 2. The lower two are Task 3 and 4.
}
\label{fig:heatmap}
\end{figure}

In Figure~\ref{fig:heatmap}, we show the $\log$ of values of Equation~\ref{eq:irl} for
different weights. We can observe the centroids of red zones move for different
tasks. It stays at the origin in Task 1, so none of target and obstacle modules
are active. It moves away from the origin when a module is active.

@@

Second, we also assumes independency between modules. Correlation between
modules doesn't impair our analysis in this paper. In Figure~\ref{fig:heatmap},
we can tell that the target module and obstacle module tend to be negatively
correlated from the shape of the red zones.

>>>>

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{rldmsubmit,palatino}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure}[h!]
\centering
\includegraphics[height=5cm]{human.jpg}
\includegraphics[height=5cm]{env.png}
\caption{(Left) A human subject with head tracker, virtual reality displayer, and
body tracker.  (Right) The environment the human can see through the displayer.
The red cubes represent obstacles. The blue balls represent targets. There is
also a gray path on the ground that the human subject can follow.}
\label{fig:avatar}
\end{figure}

Figure~\ref{fig:avatar} shows the domain that we use for the experiment. 
The agent would be punished if running into obstacles (red cubes), rewarded if
collecting targets (blue balls). There is a path on the ground that he can
follow.
Naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles.
This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.
We ask human subjects to have trackers and virtual reality displayers equipped. He
can see the envrionment through the displayer in front of his eyes. So he can
walk as if he is walking in the virtual domain.

@@

\begin{figure}[h!]
\centering
\begin{subfigure}[b]{0.24\textwidth}
\includegraphics[width=\textwidth]{task_1.png}
\caption{Path module only,\\$w = (0.039, 0.0, 0.960)$. }
\end{subfigure}
\begin{subfigure}[b]{0.24\textwidth}
\includegraphics[width=\textwidth]{task_2.png}
\caption{Obstacle + Path,\\$w = (0.081, 0.264, 0.654)$. }
\end{subfigure}
\begin{subfigure}[b]{0.24\textwidth}
\includegraphics[width=\textwidth]{task_3.png}
\caption{Target + Path, \\$w = (0.254, 0.089, 0.655)$. }
\end{subfigure}
\begin{subfigure}[b]{0.24\textwidth}
\includegraphics[width=\textwidth]{task_4.png}
\caption{Target + Obstacle + Path, \\$w = (0.215, 0.414, 0.369)$. }
\end{subfigure}
\caption{The trajectories of humans and the agent in four different tasks. The
black lines are trajectories of human subjects, and the green lines are
trajectories of the learning agent by using the optimum weights, $w$. Weights
are shown in target, obstacle, path order.}

\label{fig:exp}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{contactStats.png}
\caption{Number of targets hit and number of obstacles hit of the human subjects
and the agent.}
\label{fig:stats}
\end{figure}

Although humans don't agree each other on how to avoid obstacles or collecting
targets, the agent can figure out what the humans are doing, and perform a
similar trajectory. Figure~\ref{fig:stats} evaluates the
performance by showing the number of targets hit and number of obstacles hit.
We can observe that humans still do better than the agent in these tasks.

\begin{figure}[h!]
\centering
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=\textwidth]{objValuesTask1.png}
\caption{Path following only.}
\end{subfigure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=\textwidth]{objValuesTask2.png}
\caption{Obstacle + Path. }
\end{subfigure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=\textwidth]{objValuesTask3.png}
\caption{Target + Path. }
\end{subfigure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=\textwidth]{objValuesTask4.png}
\caption{Target + Obstacle + Path. }
\end{subfigure}
\caption{Heatmaps of the $\log$ of the values of Equation~\ref{eq:irl} for different
weights for the four tasks, respectively. The white zones indicate higher
values. The weights of all three modules sum to 1, so we only show the weights
on the target and the obstacle modules.
}
\label{fig:heatmap}
\end{figure}

In Figure~\ref{fig:heatmap}, we show the $\log$ of values of Equation~\ref{eq:irl} for
different weights. We can observe the centroids of white zones move for different
tasks. It stays at the origin in Task 1, so none of target and obstacle modules
are active. It moves away from the origin when a module is active.

@@

Second, we also assumes independency between modules. Correlation between
modules doesn't impair our analysis in this paper. In Figure~\ref{fig:heatmap},
we can tell that the target module and obstacle module tend to be negatively
correlated from the shape of the white zones.
